### 2019-04-26 README.Rmd
Added get_kegg example to README

The goal of diffEnrich is Given a List of Gene Symbols, Performs Differential 
Enrichment Ananlysis. # diffEnrich

@@

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

What is special about using `README.Rmd` instead of just `README.md`? You can include R chunks like so:

```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!

>>>>

The goal of diffEnrich is simple. Given a list of gene symbols, *diffEnrich*  will
perform differential enrichment ananlysis using the Kyoto Encyclopedia of Genes
and Genomes (KEGG) REST API. This package provides a number of functions that are 
intended to be used in a pipeline (See Figure N). Breifly, the workflow will
download and clean species specific ENTREZ gene IDs and map them to their respective
KEGG pathways by accessing KEGG's REST API. This way the user will always have 
the most up-to-date pathway data from KEGG. Next, the user will identify significantly
enriched pathways from two different gene sets, and finally, the user will identify 
pathways that are differentially expressed between the two gene sets. In addition to 
the analysis pipeline, this package also provides functions for data visualizations.

@@

First we will use the \code{get_kegg} function access the KEGG REST API and download the data sets required to perform 
our downstream analysis. This function takes two arguments. The first, \code{species} is required and is the species of 
interest. Currently, *diffEnrich* supports three species, and the argument is a character string using the KEGG
code [REF](https://www.pnas.org/content/suppl/2008/09/11/0806162105.DCSupplemental/ST1_PDF.pdf): 
Homo sapiens (human), use 'hsa'; Mus musculus (mouse), use 'mmu', and Rattus norvegicus (rat), use 'rno'. The second,
\code{path} is also passed as a character string, and is the path of the directory in which the user would like to
write the data sets downloaded from the KEGG REST API. If the user does not provide a path, the data sets will 
be automatically written to the current working directory using the \code{here::here()} functionality. These data 
sets will be tab delimited files with a name describing the data, and for reproducibility the date they were generated
and the version of KEGG when the API was accessed. In addition to these flat files, \code{get_kegg} will also
create a named list with the three relavent KEGG data sets. The names of this list will describe the the data set.

```{r get_kegg_exp1}
suppressMessages(library(diffEnrich))

## run get_kegg() using rat
kegg_rno <- get_kegg('rno')
```

Here are the files:

    kegg_to_pathway2019-04-26Release_90.0+_04-26_Apr_19.txt
    ncbi_to_kegg2019-04-26Release_90.0+_04-26_Apr_19.txt
    pathway_to_species2019-04-26Release_90.0+_04-26_Apr_19.txt

**Note:** Because it is assumed that the user might want to use the data sets generated by \code{get_kegg}, it is careful not to
overwrite data sets with exact names. \code{get_kegg} checks the path provided for data sets generated 'same-day/same-version', 
and if it finds even one of the three, it will not re-write any of the data sets. It will still however, let the user know
it is not writing out new data sets and still generate the named list object. Users can of course generate 'same-day/same-version'
data sets in different directories if they so choose.

```{r get_kegg_exp2}
## run get_kegg() using rat
kegg_rno <- get_kegg('rno')
```
